---
output:
  md_document:
    variant: markdown_github
---

# Purpose

The purpose of this README is to provide an overview to the answers for my Data Science Methods for Economics and Finance 871 Practical Exam. 

Each question is self-contained within its own folder, which is able to function on a standalone basis. The present README (the root's README) collates all individual Question folders, offering a detailed overview of what each question entails and how it has been addressed. 

The aim of this system is to ensure that I have  maintained a clear and systematic presentation of my answers, making it easier to understand and review the solutions provided.

Note: I have unzipped the data files and placed them in their respective question folders.

## Code used to get started

I used the following code to setup the root folder and the individual Question (1-5) folders. 


```{r, eval = FALSE}
fmxdat::make_project(Open = T)

CHOSEN_LOCATION <- "C:/Users/Sinead Morrow/Documents/DatSci/23597852/"
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}"), template_name = "Question1")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}"), template_name = "Question2")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}"), template_name = "Question3")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}"), template_name = "Question4")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}"), template_name = "Question5")
```


## Code Used for Figures and Tables

The following steps outline the code and procedures used to build the Texevier PDF document, including the generation of Figures and Tables. 


```{r}
rm(list=ls()) # Clear the workspace to improve the codes readability
gc() # Perform garbage collection to prompt R to return memory to operation system, this will automatically free up memory space allocated to objects which are no longer needed. 

# Load the necessary packages using pacman:
library(pacman)
p_load(tidyverse, lubridate)

# Source all functions from the code directories for each question:
list.files('Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
list.files('Question2/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
list.files('Question3/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
list.files('Question4/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
list.files('Question5/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

# Question 1: Baby Names

## Data 

### Loading the data:

```{r}

```


# Question 2: Music Taste

## Data 

### Loading the data:

```{r}

```

# Question 3: Russia - Ukraine Conflict

## Data 

### Loading the data:

```{r}

```

# Question 4: Olympics

## Data 

### Loading the data:

```{r}

```

# Question 5: SQL Queries 

## Data 

### Loading the data:

```{r}

```
